\documentclass{article}

\usepackage{hcar}

\begin{document}

\begin{hcarentry}{Real World Haskell}
\report{Bryan O'Sullivan}
\status{active development}
\participants{John Goerzen, Don Stewart}% optional
\makeheader

We are working on a book, ``Real World Haskell,'' about the practical
application of Haskell to everyday programming problems.  The book
will be published in the second half of 2008 by O'Reilly.

Our intended audience is programmers with no background in functional
languages.  We explore a diverse set of topics, among which are the
following.

\begin{itemize}
\item Basics of Haskell and functional programming
\item Developing software using standard tools like GHC and the Cabal
  packaging system
\item Code coverage, quality assurance, and performance analysis
\item Putting theory to work: working with and creating monoids,
  normal and applicative functors, monads, and monad transformers
\item Applied topics: databases, filesystems, GUI programming, web and
  other network clients, web servers
\item Concurrent, parallel, and transactional programming
\item Error handling in pure and impure code
\item Interfacing to C libraries
\item Many case studies and runnable code examples
\end{itemize}

At the time of writing (late April, 2008) we have first drafts of
about 75 per cent of the book written.  We expect it to come to about
30 chapters in total. 

We are excited to be publishing the book under a Creative Commons
License.  As we write chapters, we publish them online for people to
read and comment on, and we incorporate feedback from our readers when
we rewrite drafts of chapters.  The level of community interest has
been remarkable: so far, we have received over 4,000 comments on the
chapters we have made available.

\FurtherReading
\begin{itemize}
\item Book site: \url{http://book.realworldhaskell.org/}
\item Blog with progress and publication updates:
  \url{http://www.realworldhaskell.org/blog/}
\end{itemize}
\end{hcarentry}

\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
